Paper NA

### 2017-02-17 Paper_NA.tex
Paper with cleaned figures

The tomographic inversion results for $V_S$ and $\xi$ are presented in figures (to be defined). We divide the model description and interpretation into two parts, focusing first on the continent-wide structure and then, in more detail, on eastern different regions.

@@

\begin{figure}
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_A.pdf}}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_B.pdf}}
	\end{minipage}

@@

Our study confirms the presence of a thick cratonic root with faster than average $V_S$ down to $250km$ deep, with highest velocities, ca. $4.8km.s^{-1}$, located at depths shalower than at most $150km$. 
Laterally, the cratonic root in terms of $V_S$, coincides with precambrian aged crust. 
The western and eastern/south eastern edges follow the Rocky Mountain Front (RMF) and the Llano-Grenville Front respectively. 
The northern part is delimited by the coastine of the Arctic ocean including the arctic archipelago and Greenland. 
These lateral edges are well observed until $150km$, below, the cratonic root retracts toward the center of the archaean continent beneath Slave, Hearne/Rae and western Superior cratons. 
Everywhere within the lithosphere, a negative gradient of $V_S$ is observed with a minimum of ca. $4.6km.s^{-1}$ reached at $300km$. 
Deeper, this gradient switches to a positive trend. While the beginning of the negative gradient shows a topography, the bottom of the gradient located beneath Slave, Hearne/Rae and western Superior cratons; appears very flat.
As observed in \cite{gung2003global}; down to 250km negative anomalies of $dln(\xi)$ are observed in the whole craton in contrast with the oceanic surrounding. 
Deeper, positive anomalies are emerging beneath archaean Slave/Rae blocks and proterozoic Yavapai/Mazatzal/Great Rhyolites provinces, however $dln\xi$ anomalies remain positives beaneath the archaean Superior block. 
In the whole lithosphere, $\xi$ is higher than $1$ which means that $V_{SH} > V_{SV}$.

\subsubsection{Wyoming}{h}
\begin{figure}
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_wyoming_A.pdf}}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_wyoming_B.pdf}}
	\end{minipage}

@@

	\begin{figure}
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_slave_A.pdf}}
		\end{minipage}
		\hfill
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_slave_B.pdf}}
		\end{minipage}

@@

	\paragraph{Western part}
		\begin{figure}
			\begin{minipage}{0.5\linewidth}
				\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_west_superior_A.pdf}}
			\end{minipage}
			\hfill
			\begin{minipage}{0.5\linewidth}
				\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_west_superior_B.pdf}}
			\end{minipage}

@@

		\paragraph{Eastern part}
		\begin{figure}
			\begin{minipage}{0.5\linewidth}
				\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_east_superior_A.pdf}}
			\end{minipage}
			\hfill
			\begin{minipage}{0.5\linewidth}
				\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_east_superior_B.pdf}}
			\end{minipage}

@@

\subsubsection{Yavapai Mazatsal region}
	\begin{figure}
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_yava-maza_A.pdf}}
		\end{minipage}
		\hfill
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_yava-maza_B.pdf}}
		\end{minipage}

@@

\subsubsection{The Great Meteor track}
	\begin{figure}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_GMTrack.pdf}}

@@

\subsubsection{Gulf of Mexico}
Fast anomalies are observed beneath the whole gulf of Mexico down to $150km$ deep. Despite the proximity with pan-african lithosphere, such high velocity anomalies represent older than $150Ma$ oceanic lithosphere.

>>>>

The tomographic inversion results for $V_S$ and $\xi$ are presented in figures (to be defined). We divide the model description and interpretation into two parts, focusing first on the continent-wide structure and then, in more detail, on different regions.

@@

\begin{figure}[h]
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_A.pdf}}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_B.pdf}}
	\end{minipage}

@@

Our study confirms the presence of a thick cratonic root with faster than average $V_S$ down to $250km$ deep, with highest velocities, ca. $4.8km.s^{-1}$, located at depths shalower than at most $150km$. 
Laterally, the cratonic root in terms of $V_S$, coincides with precambrian aged crust. 
The western and eastern/south eastern edges follow the Rocky Mountain Front (RMF) and the Llano-Grenville Front respectively. 
The northern part is delimited by the coastine of the Arctic ocean including the arctic archipelago and Greenland. 
These lateral edges are well observed until $150km$, below, the cratonic root retracts toward the center of the archaean continent beneath Slave, Hearne/Rae and western Superior cratons. 
Everywhere within the lithosphere, a negative gradient of $V_S$ is observed with a minimum of ca. $4.6km.s^{-1}$ reached at $300km$. 
Deeper, this gradient switches to a positive trend. While the beginning of the negative gradient shows a topography, the bottom of the gradient located beneath Slave, Hearne/Rae and western Superior cratons; appears very flat.

As observed in \cite{gung2003global}; down to 250km low positive ($< 2\%$) anomalies of $dln(\xi)$ (Compared to an isotropic $\xi$) are observed in the whole craton. In contrast with the oceanic surrounding that shows strong positive anomalies ($> 4\%$). 
The gulf of Mexico and the southern part of Greenland show $\xi$ anomalies that are comparable to oceanic signature. 
The Grenville and Appalachian shelf (including the eastern Superior craton) show also higher $\xi$ anomalies comparable to oceanic signature. 
Deeper, positive anomalies are emerging beneath archaean Slave/Rae blocks/Eastern Superior and proterozoic North THO/Yavapai/Mazatzal/Great Rhyolites provinces, however $dln\xi$ anomalies remain low beaneath the archaean eastern Superior block. 
In the whole lithosphere, $\xi$ is higher than $1$ which means that $V_{SH} > V_{SV}$.

\subsubsection{Wyoming}
\begin{figure}[h]
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_wyoming_A.pdf}}
	\end{minipage}
	\hfill
	\begin{minipage}{0.5\linewidth}
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_wyoming_B.pdf}}
	\end{minipage}

@@

	\begin{figure}[h]
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_slave_A.pdf}}
		\end{minipage}
		\hfill
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_slave_B.pdf}}
		\end{minipage}

@@

	\paragraph{Western part}
		\begin{figure}[h]
			\begin{minipage}{0.5\linewidth}
				\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_west_superior_A.pdf}}
			\end{minipage}
			\hfill
			\begin{minipage}{0.5\linewidth}
				\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_west_superior_B.pdf}}
			\end{minipage}

@@

		\paragraph{Eastern part}
		\begin{figure}[h]
			\begin{minipage}{0.5\linewidth}
				\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_east_superior_A.pdf}}
			\end{minipage}
			\hfill
			\begin{minipage}{0.5\linewidth}
				\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_east_superior_B.pdf}}
			\end{minipage}

@@

\subsubsection{Yavapai Mazatsal region}
	\begin{figure}[h]
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_yava-maza_A.pdf}}
		\end{minipage}
		\hfill
		\begin{minipage}{0.5\linewidth}
			\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_yava-maza_B.pdf}}
		\end{minipage}

@@

\subsubsection{The Great Meteor track}
	\begin{figure}[h]
		\centerline{\includegraphics[width=\linewidth]{figures/profiles_NASEM3_vs_dxi_GMTrack.pdf}}

@@

% \subsubsection{Gulf of Mexico}
% Fast anomalies are observed beneath the whole gulf of Mexico down to $150km$ deep. Despite the proximity with pan-african lithosphere, such high velocity anomalies represent older than $150Ma$ oceanic lithosphere.
